A Novel Comprehensive Quality Evaluation Model in Automated Semantic Web Service Composition

### 2016-10-20 paper.tex
update

 \item To evaluate the performance of proposed approaches, we utilise the datasets from Web Services Challenge 2009 (WSC'09) \cite{kona2009wsc}.
\end{enumerate}

@@

\subsection{Fitness Calculation}
The fitness value is calculated from the aggregate value of quality components involved in a graph-based service composition. A weighted sum of those components is utilised in the fitness function \ref{equation7}, in which fitness value of 1 means the best overall quality and 0 means the worst. In addition, aggregate value of each parameters must be normalised between 0 and 1. In details, $MT$, $S$, $A$, $R$, $T$, and $C$ are normalised in Formula \ref{equation8}.

@@

\noindent where $\sum_{i=1}^{6} w_i = 1$
\\\\
\begin{equation}
\label{equation8}
N(Q_{k}) = 
\begin{cases}
	\frac{value - min}{max - min} & \text{ if }max - min \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}

\section{Experiment Design}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design. The objective of the evaluation are: 1) measure the effectiveness of the proposed comprehensive quality model in automated semantic web service composition approach, and explore the impact of the semantic matchmaking that contributes to overall composition quality. 2) compare the optimised solutions with using comprehensive evaluation model with using QoS-aware evaluation model to reveal the advantages of our novel method.

We utilise the web service challenge 2009 (WSC’09) web service data sets to perform a standard evaluation. Compared to previous web service challenge dataset, WSC'09 is evolved with OWL for providing richer semantics. With an incremental number in concept, individuals and web services in each dataset, it is a proper dataset for the scalability measures in our defined quality evaluation model.Table 1 presents the features of the WSC’09 dataset. The number of concepts, individuals in the ontology and services of each data set is shown in the second, third, fourth column respectively. Also, we extend the all the datasets with QoS attributes from service providers to perform a comprehensive quality evaluation. 
\begin{table}[]
\centering
\caption{features of the WSC'09 datasets}
\label{wsc09datasetTable}
\begin{tabular}{|l|l|l|l|}
\hline
\multicolumn{1}{|c|}{Dataset} & No.Concept & No.Individual & No.Service \\ \hline
WSC'09 01                     & 1578       &3102           &572      \\ \hline
WSC'09 02                     & 12388      &24815          &4129      \\ \hline
WSC'09 03                     & 18573      &37316          &8138      \\ \hline
WSC'09 04                     & 18673      &37324          &8301      \\ \hline
\end{tabular}
\end{table}

We run the experiment under computing grid comprising of almost 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine. Experimentation was done using the composite service approach explained in Section \ref{qswsc_approach}, and evaluated in the comprehensive quality model introduced in Section \ref{qualityModel}. The parameters were chosen based on general settings from \cite{shi2001particle}, In PSO approach, 30 particles evolved in 100 generations in the searching space, in which problem dimension's size equals to the relevant service size shown in graph. we run 30 times independently for each dataset. In addition, weights setting are more flexible defined by users' preferences. Simply, we configure weights of fitness function as same leverage for balancing functional side and nonfunctional side. Therefore, W1 and W2 are equals to 0.1 and 0.4 entirety 0.5,  and W3, W4, W5, W6 are all set to 0.125 summed 0.5.

\section{Results and Analysis}\label{results_analysis}
\subsection{Convergence Test}\label{convergenceTest}
The purpose of our experiment is to expose the results of our proposed approach are optimised comprehensive quality for web service challenge tasks utilising datasets from WSC’09. To study an overall effectiveness of evaluation model and investigate the impacts of all involved components that are contributing the weighted sum fitness functional. We analysis all the performance of these components in the whole evolutionary process in Figure \ref{exp_fitnessvalue}, in which the three tasks' experiment results are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average quality of service for generation 0-99 with optimum.
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{convergency.pdf}}}
 \caption{Average fitness, Average MatchType quality, Average Similarity quality and Average QoS per generation with comprehensive quality optimum}
 \label{exp_fitnessvalue}
\end{figure}

@@

Lastly, It is interesting to look at the average QoS per generation for the 30 independent runs if the behaviour of functional part performance is towards a higher value, where QoS is the value corresponding to the best fitness so far found in each generation. We construct the results in the fourth groups in Figure \ref{exp_fitnessvalue}. It is obviously that the overall trend of QoS moves upward in three tasks, and reach almost constant later on. Luckiely, we reach a very good state for QoS value, because we don't see too much trade-off from QoS regarding the improvement in functional quality part.

\subsection{Comparision Test}\label{comparisionTest}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=8cm]{wscs.pdf}}}
 \caption{Example composition solutions for problem1 WSC'09.}
 \label{wscs}
\end{figure}
We defined our optimised web service composition as $WSC = (V, E)Graph$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of service connections as edges associated matchType quality and semantic similarity quality: $E = {e_{1}, e_{2},... e_{n}}$ where $e1$ is define as $(S_{1},S_{2})={q_{mt}, q_{s}}$. Here we provide an uncomplicated example of the web service composition solution to problem1, which can be described in the Figure \ref{wscs}. The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, $q_{mt}$ and $q_{s}$) are calcuated for all edges ${e_{1}, e_{2},... e_{n}}$, and further aggregateed in $Q_{mt}$ and $Q_{s}$ respectively.In addtion, $Q_{QoS}$ is calcuated the all the non-functional attributes of $V$ using aggregation rules defined before.

After well-defined solutions are discussed, we will look at $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ using  black-box testing for sollution comparision, where these components in both comprehensive quality evaluation approach and traditional QoS-ware one \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} are compared to reveal how good our evaluation mode is. In a decision table \ref{decisionTable}, these two models are interpreted as a rule set considering three different conditions (three independent tasks) associated with three corresponding sollutions. In each sollution, we compare $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$, where $Q_{QoS}$ is normalised to make them comparable from 0 to 1 in our method. From the table below.

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\footnotesize
\centering
\caption{Quality of two evaluation model in a decision table}
\label{decisionTable}
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{\multirow{2}{*}{}}                              & Rule 1               & Rule 2                           \\ \cline{3-4} 
\multicolumn{2}{|c|}{}                                               & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
\multirow{3}{*}{Condition}            & dataset1             & $\surd$              & $\surd$                            \\ \cline{2-4} 
                                      & dataset2             & $\surd$              & $\surd$                            \\ \cline{2-4} 
                                      & dataset3             & $\surd$              & $\surd$                            \\ \hline
\multirow{3}{*}{\shortstack{Task1\\Optimised sollution}}  &$Q_{mt}$                      & .232635              & .232635                          \\ \cline{2-4} 
                                      &$Q_{s}$                       & .903572              & .903572                          \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .578577              & .578577                          \\ \hline
\multirow{3}{*}{\shortstack{Task2\\Optimised sollution}}  &$Q_{mt}$                      & .001828              & .000851$\downarrow$               \\ \cline{2-4} 
                                      &$Q_{s}$                       & .917172              & .938840$\uparrow$                 \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .480251              & .473002$\downarrow$               \\ \hline
\multirow{3}{*}{\shortstack{Task3\\Optimised sollution}}  &$Q_{mt}$                      & .191188              & .247836$\uparrow$                  \\ \cline{2-4} 
                                      &$Q_{s}$                       & .951509              & .973723$\uparrow$                  \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .493927              & .491538$\downarrow$                         \\ \hline
\end{tabular}
\end{table}
From the table \ref{decisionTable}, Task 1 represents the same solution that can be observed in values of  $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$ using the smallest dataset size with the lowest complexity of ontologies and valid solutions. However, we can recognise trade-offs in task2 and task3 using our evaluation model, where a 0.021668 increase and a 0.00098 decrease in similarity quality and matchType quality with weights 0.4 and 0.1 respectively so that it is still considered to be an improvement in functional quality part with a trade-off value 0.007249 in QoS. In task3, the benefit of functional part quality is clearer with an increase in both similarity quality and matchType quality of 0.056648 and 0.078862 while a slight decrease in QoS.  In conclusion, we can perceive that our evaluation could find out better functional quality with a reasonable trade off in QoS.

>>>>

 \item To evaluate the performance of proposed approaches, we utilise the datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
\end{enumerate}

@@

\subsection{Fitness Calculation}
The fitness value is calculated from the aggregate value of quality components involved in a graph-based service composition. A weighted sum of those components is utilised in the fitness function \ref{equation7}, in which fitness value of 1 means the best overall quality and 0 means the worst. As the sum of all the function weights (w1 to w6) is equal to 1, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised ranging from 0 to 1 so that the overall result falls within 0 to 1. Also, the lowest T and C value represent the best quality so that the objective function is offset using $(1 - T)$ and $(1 - C)$.

@@

\noindent where $\sum_{i=1}^{6} w_i = 1$

\section{Experiment Design}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design. The objectives of the evaluation are to measure the effectiveness of the proposed comprehensive quality model in automated semantic web service composition approach, and to explore the impact of the semantic matchmaking that contributes to overall composition quality, and to compare solutions generated by QoS-ware approach with our method.

We utilise benchmark dataset web service challenge 2009 (WSC09) \cite{kona2009wsc} web service data sets to perform a standard evaluation. WSC09 designed OWL for providing richer semantics consisting tasks with variable size. With an incremental number in concept, individuals and web services in each dataset, it is a proper dataset for the scalability measures in our defined quality evaluation model. Table \ref{wsc09datasetTable} presents the features of the WSC’09 dataset. The number of concepts, individuals in the ontology and services of each data set is shown in the second, third, fourth column respectively. Also, we extend all the datasets with QoS attributes from service providers to perform a comprehensive quality evaluation. 
\begin{table}[]
\centering
\caption{Features of the WSC09 datasets}
\label{wsc09datasetTable}
\begin{tabular}{|l|l|l|l|}
\hline
\multicolumn{1}{|c|}{Dataset} & No.Concept & No.Individual & No.Service \\ \hline
WSC09 01                     & 1578       &3102           &572      \\ \hline
WSC09 02                     & 12388      &24815          &4129      \\ \hline
WSC09 03                     & 18573      &37316          &8138      \\ \hline
WSC09 04                     & 18673      &37324          &8301      \\ \hline
WSC09 05                     & 31044      &62132          &15211    \\ \hline
\end{tabular}
\end{table}

We run the experiment under computing grid comprising of almost 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine. Experimentation was done using the approach explained in Section \ref{qswsc_approach}, and evaluated in the comprehensive quality model introduced in Subsection \ref{qualityModel}. The parameters were chosen based on general settings from \cite{shi2001particle} for our PSO-based approach, 30 particles evolved in 100 generations in the searching space, in which problem dimension's size equals to the relevant service size shown in graph. we run 30 times independently for each dataset. In addition, weights setting are flexibly defined by users' preferences. As part of their requirement, we configure weights of fitness function as the same to properly balance functional side and nonfunctional side. Therefore, $w_{1}$ and $w_{2}$ are equals to 0.1 and 0.4,  and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly.

\section{Results and Analysis}\label{results_analysis}
\subsection{Convergence Test}\label{convergenceTest}
To analysis the effectiveness of our approach, we explore the convergency rate of the proposed method in this section. We show the convergency of five tasks in WSC09. To further study an overall effectiveness of evaluation model and investigate the impacts of all involved components in the fitness function. We analysis all the performance of these components in the whole evolutionary process in Figure \ref{exp_fitnessvalue}, in which the five tasks' experiment results are arranged in four groups consisting of average fitness, average matchType quality, average similarity quality and average quality of service for generation 0-99 with optimum.
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=12cm]{convergency.pdf}}}
 \caption{Average Fitness, Average MatchType Quality, Average Similarity quality and Average QoS per generation with comprehensive quality optimum}
 \label{exp_fitnessvalue}
\end{figure}

@@

Lastly, It is interesting to look at the average QoS per generation for the 30 independent runs if the behaviour of functional part performance is towards a higher value, where QoS is the value corresponding to the best fitness so far found in each generation. We construct the results in the fourth groups in Figure \ref{exp_fitnessvalue}. It is obviously that the overall trend of QoS moves upward in three tasks, and reach almost constant later on. Luckily, we reach a very good state for QoS value, because we don't see too much trade-off from QoS regarding the improvement in functional quality part.

\subsection{Comparision Test}\label{comparisionTest}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=8cm]{wscs.pdf}}}
 \caption{Example composition solutions for problem1 WSC'09.}
 \label{wscs}
\end{figure}
We defined our optimised web service composition as $WSC = (V, E)Graph$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of service connections as edges associated matchType quality and semantic similarity quality: $E = {e_{1}, e_{2},... e_{n}}$ where $e1$ is define as $(S_{1},S_{2})={q_{mt}, q_{s}}$. Here we provide an uncomplicated example of the web service composition solution to problem1, which can be described in the Figure \ref{wscs}. The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, $q_{mt}$ and $q_{s}$) are calculated for all edges ${e_{1}, e_{2},... e_{n}}$, and further aggregated in $Q_{mt}$ and $Q_{s}$ respectively.In addtion, $Q_{QoS}$ is calculated the all the non-functional attributes of $V$ using aggregation rules defined before.

After well-defined solutions are discussed, we will look at $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ using  black-box testing for solution comparision, where these components in both comprehensive quality evaluation approach and traditional QoS-ware one \cite{feng2013dynamic,huang2009effective,ma2015hybrid,da2014graph} are compared to reveal how good our evaluation mode is. In a decision table \ref{decisionTable}, these two models are interpreted as a rule set considering three different conditions (three independent tasks) associated with three corresponding solutions. In each solution, we compare $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$, where $Q_{QoS}$ is normalised to make them comparable from 0 to 1 in our method. From the table below.

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\footnotesize
\centering
\caption{Quality of two evaluation model in a decision table}
\label{decisionTable}
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{\multirow{2}{*}{}}                              & Rule 1               & Rule 2                           \\ \cline{3-4} 
\multicolumn{2}{|c|}{}                                               & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
\multirow{3}{*}{Condition}            & dataset1             & $\surd$              & $\surd$                            \\ \cline{2-4} 
                                      & dataset2             & $\surd$              & $\surd$                            \\ \cline{2-4} 
                                      & dataset3             & $\surd$              & $\surd$                            \\ \hline
\multirow{3}{*}{\shortstack{Task1\\Optimised solution}}  &$Q_{mt}$                      & .232635              & .232635                          \\ \cline{2-4} 
                                      &$Q_{s}$                       & .903572              & .903572                          \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .578577              & .578577                          \\ \hline
\multirow{3}{*}{\shortstack{Task2\\Optimised solution}}  &$Q_{mt}$                      & .001828              & .000851$\downarrow$               \\ \cline{2-4} 
                                      &$Q_{s}$                       & .917172              & .938840$\uparrow$                 \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .480251              & .473002$\downarrow$               \\ \hline
\multirow{3}{*}{\shortstack{Task3\\Optimised solution}}  &$Q_{mt}$                      & .191188              & .247836$\uparrow$                  \\ \cline{2-4} 
                                      &$Q_{s}$                       & .951509              & .973723$\uparrow$                  \\ \cline{2-4}
                                      &$Q_{QoS}$                     & .493927              & .491538$\downarrow$                         \\ \hline
\end{tabular}
\end{table}
From the table \ref{decisionTable}, Task 1 represents the same solution that can be observed in values of  $Q_{mt}$,$Q_{s}$ and $Q_{QoS}$ using the smallest dataset size with the lowest complexity of ontologies and valid solutions. However, we can recognise trade-offs in task2 and task3 using our evaluation model, where a 0.021668 increase and a 0.00098 decrease in similarity quality and matchType quality with weights 0.4 and 0.1 respectively so that it is still considered to be an improvement in functional quality part with a trade-off value 0.007249 in QoS. In task3, the benefit of functional part quality is clearer with an increase in both similarity quality and matchType quality of 0.056648 and 0.078862 while a slight decrease in QoS.  In conclusion, we can perceive that our evaluation could find out better functional quality with a reasonable trade off in QoS.
